User-level Grid Monitoring with Inca 2

### 2007-02-26 papers/hpdc-gmw-2007/paper.tex
modifications to TeraGrid section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6555 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Describe CTSS

TeraGrid's Coordinated TeraGrid Software and Services (CTSS) was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS is available from all TeraGrid compute resources and is
comprised of approximately 30 software packages for Grid services (gridftp, ws
gram), Grid jobs (gridshell, myproxy, globus), cluster tools (pacman, tgusage),
data management (srb, hdf5) and user applications (mpich, gcc).

In order to validate and verify CTSS functionality from a user perspective,
TeraGrid and SDSC developed and deployed Inca 1 on TeraGrid in 2003. TeraGrid
transitioned to Inca 2 in 2006 and, in addition to CTSS monitoring, began using
Inca to collect job usage information from Globus 2 GRAM logs and to detect
expired host and CA certificates and CA CRLs to its Inca deployment.

% Describe reporters, configuration, and deployment.  Figure.

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.

% Consumer view of CTSS, security, etc.

TeraGrid currently has six status pages: a summary of software stack test
failures, a detailed grid of software test results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.5]{status-page.eps}
  \caption{TeraGrid CTSS status page.}
  \label{status_page_fig}
\end{figure}

>>>>

% Description and Requirements - Describe CTSS
Requirements for user-level Grid monitoring on TeraGrid initially included the
validation and verification of CTSS on each resource.  As described in the
introduction, CTSS was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
resources and is comprised of approximately 30 software packages that provide
Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
Inca was originally
deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
to collect job usage information from Globus 2 GRAM logs and to detect expired
host and CA certificates and CA CRLs.

% Usage of Inca - Describe reporters, configuration, and deployment.  Figure.
To provide user-level monitoring of CTSSv3, a number of version and unit
test reporters were developed to test the software packages in CTSS.
Currently, there are 56 such reporters executing an average of 109 series on
each of TeraGrid's 18 resources.  They include 48 all-to-all tests (GSI-SSH,
GRAM, and GridFTP), 20 Grid-related tests, 28 data-related tests, 30
application tool-related tests, and 2 security-related tests.  
Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 deployment
configuration.  The
agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on inca.sdsc.edu.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.6]{tg-deploy.eps}
  \caption{TeraGrid's Inca 2 Deployment.}
  \label{tg_deploy_fig}
\end{figure}

% Results - Consumer view of CTSS, security, etc.
TeraGrid currently has six status pages to display the Inca monitoring
information: a summary of CTSSv3 test failures, a detailed grid of CTSSv3 test
results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSSv3 
test result
page.  CTSSv3 software packages are listed along the column and TeraGrid
resources (anonymized) in the header rows.  Test results for each package and
resource are shown in the table body rows.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.4]{status-page.eps}
  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
  resources anonymized.}
  \label{status_page_fig}
\end{figure}
